\documentclass[10pt,a4paper]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\definecolor{darkblue}{RGB}{0,0,102}

\titleformat{\section}{\normalsize\bfseries\color{darkblue}}{}{0em}{}[\titlerule]

\setlist[itemize]{noitemsep, topsep=2pt, left=1.5em}
\titlespacing\section{0pt}{6pt}{3pt}

\pagenumbering{gobble}
\hypersetup{colorlinks=true, urlcolor=darkblue, linkcolor=darkblue}

\begin{document}

\noindent
{\LARGE \textbf{Kshitiz Chaurasia}}\\
Product Manager | Fintech \& AI Products | IIT Kanpur\\
\href{mailto:kshitiz.iitk@gmail.com}{kshitiz.iitk@gmail.com} | +91-9307930008 | \href{https://linkedin.com/in/hellokshitiz}{linkedin.com/in/hellokshitiz} | Bengaluru, India

%-----------------------------------
\section*{Professional Summary}

Product leader operating at founder level. Owned and scaled a fintech vertical as the sole PM and grew into the de-facto product head within months. Reduced execution cycles by 60 to 70 percent by building production-grade features independently and influencing company-level product bets.

Built AI-first products including an industry-first portfolio review agent. Strong mix of product thinking and hands-on execution, with consistent impact across growth, compliance, and platform efficiency.

%-----------------------------------
\section*{Experience}

\noindent\textbf{Lead Product Manager – Wealthy} \hfill \textit{Mar 2025 – Present}
\vspace{-3pt}
\begin{itemize}
  \item Owned and scaled the Partner Experience vertical across mobile and web as the sole PM. Set roadmap, drove execution, and worked directly with Founder and CTO on product strategy.
  
  \item Introduced a prototype-first development approach by building production-ready features independently. Reduced shipping cycles by \textbf{60 to 70\%}.
  
  \item Built and launched the \textbf{industry’s first AI-powered portfolio review agent}, improving how partners analyze and act on client portfolios.
  
  \item Leading AI-driven workflows such as portfolio assistants, planning copilots, conversational interfaces, and payout automation to improve partner productivity and revenue flow.
\end{itemize}

\noindent\textbf{Product Manager – AssetPlus} \hfill \textit{Jan 2023 – Mar 2025}
\vspace{-3pt}
{\small Joined as the only PM and quickly became the central product owner working directly with the co-founder and CTO across all major decisions.}
\vspace{2pt}

\begin{itemize}
  \item Became the go-to product decision maker across teams. Senior stakeholders relied on my judgment for critical product choices.
  
  \item Promoted from APM to PM in 12 months through ownership across multiple product lines.
  
  \item Built internal analytics systems from scratch by self-learning the stack. Delivered dashboards overnight and sped up decision making across teams.
  
  \item \textbf{Key product outcomes:}
  \begin{itemize}
      \item Change of Broker enabled \textbf{Rs. 250 Cr} AUM transfers in 4 months
      \item SIP Top-Up reached 12 to 15\% adoption with \textbf{Rs. 7.8 Cr ARR} in month one
      \item Loans Against Mutual Funds disbursed \textbf{Rs. 1.6 Cr} in 30 days
  \end{itemize}
  
  \item \textbf{Core system improvements:}
  \begin{itemize}
      \item KYC via Digilocker reduced activation time to 0 to 5 minutes and lowered rejection rates by 15\%
      \item CAS imports reduced from 4 to 5 minutes to 30 seconds and increased usage by 800\%
      \item Folio updates for 100k+ users reduced from 10 to 15 days to 2 minutes
  \end{itemize}
  
  \item \textbf{Compliance and scale:}
  \begin{itemize}
      \item Completed SEBI KYC for 25k+ investors protecting \textbf{Rs. 200+ Cr}
      \item Enabled nomination updates for 100k+ users safeguarding \textbf{Rs. 50+ lacs}
      \item Maintained zero compliance failures across all launches
  \end{itemize}
\end{itemize}

\noindent\textbf{Associate Product Manager – Zomato} \hfill \textit{Jun 2022 – Nov 2022}
\vspace{-3pt}
\begin{itemize}
  \item Reduced \textbf{Rs. 2 Cr} annual costs by migrating support systems. Projected \textbf{Rs. 8 Cr} long-term savings.
  
  \item Built core ticketing systems including automations, routing, and dashboards that improved support operations.
  
  \item Redesigned chatbot flows leading to savings of \textbf{Rs. 62 lacs per month}.
  
  \item Built and launched Zomaland chatbot end to end. Led a team of 4 to build a smartwatch app and secured 3rd place at an internal hackathon.
\end{itemize}

%-----------------------------------
\section*{Education}

\textbf{B.Tech – Indian Institute of Technology, Kanpur} \hfill 2018 – 2022 \\
CPI: 8.3

%-----------------------------------
\section*{Skills}

Product Strategy | 0 to 1 Products | AI and LLM Product Design | Fintech | Growth Systems | SQL | User Research | A/B Testing | Analytics | SEBI Compliance | Agile

\end{document}